An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-11 poly-embed-journal/poly-embed-journal.tex

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours}
For $\alpha \in (0,1)$, \citet{ramaswamy2018consistent} study the loss $\ell^\alpha : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^\alpha(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\raft{Why do we have $\ell^\alpha$, $\psi^\alpha$ (superscripts) but $L_\alpha$ (subscript)?  Ideally we could make them uniform, but I wasn't sure what the considerations were}
%\jessiet{No good reason, at the very least. I changed it.  \#burn}
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
For the case $\alpha=1/2$,
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L^{1/2}$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
Letting $d = \ceil{\log_2(n)}$, their surrogate $L^{1/2} : \reals^d \to \reals^\Y_+$ is given by
\begin{equation}\label{eq:abstain-surrogate}
L^{1/2}(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L^{1/2}$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
The authors show that the link $\psi^{1/2}$ is calibrated\jessiet{IIRC, they actually show this a bit more generally.  basically, they show any $\epsilon$-separated link with $\| \cdot \|_\infty$ works.  Changing in text, but happy to revert.}, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\epsilon}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
% can be used to verify the calibration of the prposed link.
%\jessiet{changed this sentence.  Thoughts?}\raft{Changed it back, since I think our narrative here is that our framework would have simplified their paper}
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L^{1/2},\psi^1)$ with respect to $\ell^{1/2}$. 
%\jessiet{does it?  do we know $\epsilon$ is small enough for higher $d$?}\raft{removed ``immediately'' since you're right there are details to work out, but I'm pretty sure $\epsilon=1$ should hold for all $d$}
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}

>>>>

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours}
\citet{ramaswamy2018consistent} study the loss $\ell: [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
Letting $d = \ceil{\log_2(n)}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
\begin{equation}\label{eq:abstain-surrogate}
L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. \jessiet{Remove this sentence?  or new paragraph below?}
The authors show that the link $\psi^{\infty}$ is calibrated, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\infty}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L^{1/2},\psi^{1/2})$.

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\epsilon}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
% and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
%(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
Hence, our framework could have simplified the process of finding $\psi^{1/2}$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{check whether our bounds match}).
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}
